### 2021-11-09 Final Doc/Chapters/Chapter2.tex
Final Push

This current paradigm of education is operated on the basis of standardisation to accommodate the change in societal needs and requirements that the industrial age brought with it (\cite{Reigeluth1996}). Reigeluth (1996) states that this system was developed on the fundamental need of sorting students into different categories and to allow for comparisons so that the training of the workforce could also be separated into different groups, those being labourers, having “hands-on” skills, and managers, who mainly had a managerial skill set. 
\\\\
However, with the shift into the “information age”, the requirements of the workforce have also changed. The industrial age being a time of mass-production with the emergence of various new processing technologies and the information age being characterised by the fact that information is being transmitted and generated at an ever-increasing rate due to further technological developments (\cite{gibson2006games, Reigeluth1996}). The most notable changes from the aforementioned paradigm shifts are that from conformity and compliance to initiative and diversity where greater value is placed on each individual’s strength and contribution to a project or organisation rather than each individual having the same skill set (\cite{Reigeluth1996}).  A few other differences between the needs of organisations during the industrial age and the new requirements brought with the information age are depicted in the above table.
\newpage
\noindent Reigeluth (1996) continues and states that the current paradigm is not focused on learning but rather categorisation. Ackoff (1991) hold a similar viewpoint stating that there is more of a focus on teaching rather than learning. It should be noted that teaching and learning are very distinct from one another as both can take place without the other (\cite{Ackoff1991}). Learning is defined as increasing one’s ability to perform an act effectively while trying to meet an objective through acquiring new knowledge whereas teaching is the process of providing this knowledge (\cite{Ackoff1991}). Through this, it is clear that institutions under this paradigm aim to give learners a verbose vocabulary to speak on topics that they do not fully comprehend (\cite{Ackoff1991}). 
\\\\
Due to this aforementioned paradigm shift and in what requirements are desired by most organisations in the information age, a shift in instructional theory is also needed – one such as going from making use of passive learning through traditional teaching means to one that is centred on active learning (\cite{Reigeluth1996}). These changes are discussed in more detail in the following section on pedagogy and learning theories and the means to accomplish them in the further sections on ludology and gamification.

@@

\subsection{Learner's at the Core of Learning}
Some instructional theories focus on students learning with minimal interaction with a teacher or instructor. Reigeluth (1996) refers to the learning methods that follow his ideology as ones where an instructor acts as an indirect guide to a class of learners instead of the typical “sage on the stage” structure of a lecture or presentation. 
\\\\\\
Two of these aforementioned theories are learning by doing and learning by teaching methods. Learning by doing functions on the principle that skills can be improved through practice and self-perfection on a particular topic or knowledge base (\cite{Fisch2009}). This means of instruction has become increasingly popular amongst companies where they are able to make use of “on the job” training as it allows for a person to be productive immediately as well as become more proficient at tasks gradually (\cite{Fisch2009}). The learning by teaching method works under the assumption that learners are able to increase their understanding of a certain topic by teaching it to other learners (\cite{Fisch2009}). This method of learning has garnered more usage recently as it is a viable means of learning in environments with too few teachers or instructors and increases the overall learning process (\cite{Fisch2009}). As shown in the following table, learning methods that place the learner in control are very flexible and as such can be incorporated when attempting to teach various and different fields or subjects (\cite{Ackoff1991}).

@@

\noindent The third principle, Demonstration, proposes that learning takes place when the activities that are undertaken impart the knowledge instead of stating the information (\cite{Merrill2002}). “Demonstration consistency” explains that any examples or visualisation should be kept in line with the original learning goals (\cite{Merrill2002}). The next is “Learner Guidance” and states that learners should be shown where the relevant information for problems can be found be it in the form of comparative examples or various representation of one source (\cite{Merrill2002}). “Relevant Media” explains that when media is used as a means of demonstration, different types can be used provided that they do not fight for a learner’s attention (\cite{Merrill2002}).
\\\\
The fourth principle is Application which states that learning takes place when learners actively solve problems with the new knowledge they have acquired (\cite{Merrill2002}). “Practice Consistency” is similar to Demonstration consistency but with a focus on the application of knowledge (\cite{Merrill2002}). “Diminishing Coaching” is where the learners are provided with relevant feedback, but it is slowly lessened over time (\cite{Merrill2002}). It is also important that the problems provided to learners for practice have a good variety, as explained as “Varied Problems” (\cite{Merrill2002}).
\\\\
The fifth, and final, principle is Integration which is when the knowledge a learner has acquired is used by them in their everyday life (\cite{Merrill2002}). The first corollary, “Watch Me”, explains that learners are provided to showcase the new knowledge or skill they have acquired (\cite{Merrill2002}). “Reflection” deals with giving learners time to be able to debate with others on the topic involved (\cite{Merrill2002}). Lastly, “Creation” states that learners should be able to make use of their new knowledge or skill in some personal capacity (\cite{Merrill2002}).
\\\\
The principles and corollaries provided by Merrill (2002) provide an expansive and detailed structure to be used when developing any learning opportunity making it an exceptional choice to adapt specifically to a digital game learning system.  It does, however, lack a comprehensive discussion on how to keep learners engaged with the content and, as such, the next subsection will discuss some theories pertaining to the role of motivation in learning.

@@

\subsection{The Influence of Motivation}
A learner's motivation is what will drive them to engage with and enjoy the content being studied. This motivation can come in one of two forms according to Kapp (2012a) and to better understand the theories focussed on learner motivation, this distinction will be discussed first.
\\\\
The first is intrinsic motivation which is any motivation aimed to accomplish something and has originated from a desire to do something for oneself (\cite{Kapp2012a}). Thus, the motivation comes from the learner. On the other hand, with extrinsic motivation, the drive and desire to accomplish a task of some kind stems from wanting some form of reward or avoiding punishment of some kind (\cite{Kapp2012a}). Thus, motivation is created in return for something, either tangible or otherwise. 
\\\\
One model for motivating learners is the ARCS Model which was developed by John Keller (1987) which is frequently referenced in the aforementioned field of instructional design (\cite{Kapp2012a}). It is comprised of four main elements with each focusing on designing instruction in a different way (\cite{Kapp2012a, keller1987development}). 
\\
The first of these is Attention and it is an element that is concerned with gaining and then keeping the learners’ interest. There are three main methods to accomplish this with the first being gaining attention through the use of relatable examples or surprise. The next is to create curiosity within the learners through means such as role-playing or hands-on examples. The last means to keep attention is the variability which means periodically changing the method of delivery (\cite{Kapp2012a, keller1987development}).
\\\\
Relevance refers to having the content be relevant to the learner and Kapp (Kapp2012a) mentions that this can be done through orienting the environment around achieving goals, creating a link between the motives of learners and that of the instruction means, displaying that the content is in somewhat familiar to the learners and finally developing a model of the results of learning the presented knowledge (\cite{keller1987development}).
\\\\
Another element of this model, Confidence, is the expectations of success set by the learner and as such when they meet these expectations they are confident in their ability to do the work (\cite{Kapp2012a, keller1987development}). This can be aided by providing learners with clear expectations and requirements upfront about the skill or knowledge. It is also helpful to provide smaller opportunities to succeed as with each success the learners will become more confident (\cite{Kapp2012a, keller1987development}).
\\\\
The last element in the ARCS model is Satisfaction and is concerned with giving learners a sense of accomplishment and that the effort in the learning process has some value and weight to it (\cite{Kapp2012a, keller1987development}). This can be accomplished by allowing learners to see how their new-found knowledge can be used, either through the use of a real-world demonstration or via some form of simulation (\cite{Kapp2012a, keller1987development}).
\\\\
This section has detailed three aspects found within pedagogy, instructional design and learning theories each providing some insight into effectively transferring and imparting knowledge to a learner. Placing the learner at the centre of both teaching and learning allows for great flexibility in how to present that given material while Merrill (2002) provides an expansive framework to structure this presentation of knowledge whereas Kapp (2012a), through citing John Keller, explains ways to keep learners motivated throughout the learning process.

@@

\subsection{Serious Games}
Annetta (2008) states that the movement to include video games in teaching and training began in 2003, two years after the field of ludology began to gain traction itself concerning digital and computer-based games. The types of games used in this context are often referred to as “serious games”.  
\\\\
“Serious games” were introduced as digital concepts in 2002 through the Serious Game Initiative which was spearheaded by David Rejeski and Ben Sawyer (\cite{DeGloria2014}). The initial intention for serious games was for them to be used as a means of training certain tasks and skills (\cite{DeGloria2014}) – this was typically done through simulation type games which will be discussed in the following subsection in greater detail.
\\\\
Virvou, Katsionis and Manos (2005) mention that the endeavour to create serious games has yet to reach schools due to certain criticisms about games in general that hinders this. This is due to the fact that discussions around games by educators have largely focused on the social consequences of playing games instead of the educational potential games hold (\cite{Squire2003}). Due to this the study of serious games became more theoretical and discussion-based at lower levels and more applied with actual use at higher levels. This can be seen by implementations implemented in several fields including medical rehabilitation, ecological studies, learning languages and business studies (\cite{Burke2009, Costanza2014, Ranalli2008, Tao2009}). 
\\\\
These types of games have already had an impact on the military, medical and higher business education fields early in their conception and this trend continues to this day with most serious games being used within the medical fields specifically (\cite{Annetta2008, DeGloria2014}). However, there were attempts to use serious games, as simulations, within physics and engineering (\cite{Deshpande2011}).

\subsection{Games as Simulation}
Games have also found use as a means to simulate models, environments and a myriad of other systems. As mentioned in the previous subsection, there are a few games used for medical training (\cite{Burke2009}) and to be effective at teaching and demonstrating these topics, digital games need to be used as a simulation.
\\\\
Squire (2003) provides a definition for games as a simulation and states that these simulations attempt to model reality in a consistent manner usually through modelling physical or social systems through another system – which in this case would be a computer and the digital video game. There are two main types of simulations, Hi-fidelity and low fidelity. Hi-fidelity simulations attempt to model every possible interaction in a given system, phenomena or environment as accurately as possible (\cite{Squire2003}). In contrast, a low fidelity simulation will make use of a fair bit of abstraction as it aims to only demonstrate a few key characteristics of the phenomena or environment (\cite{Squire2003}). Games as simulations would comprise of both of these types depending on the content that it attempts to simulate,
\\\\
Deshpande and Huang (2011) describe the use of games as a means of simulation for specific sections of work in physics and engineering courses as an addition to traditional teaching as it provides a relatively simple way to demonstrate certain phenomena. As such these authors discuss the simulation aspect of games rather than the narrative as when dealing with a simulation digital game it typical lacks most narrative elements in the traditional sense (\cite{Deshpande2011}).
\\\\
This section detailed the field of ludology and its roots in the “spirit of play” amongst cultures and society as well as the shift into being an academic means to study digital computer games. Through this, it was able to describe and develop the idea of a “serious game” and consequently games as simulations which are the most effective means to convey a learning environment through video games as a whole. Following this section, this study discusses how to link the learning theories of the previous section and the study of games together through a specific discussion on gamification.

@@

\item Psychomotor Domain deals with making use of cognitive knowledge through physical skills (hand-eye coordination is an example of this) and is most effectively taught through observation.
\end{itemize}
Gamification makes use of several procedures and processes that are rooted in various academic theories, most notably ones found within pedagogy and as such was discussed in the pedagogy section of this literature review (\cite{KappArticle2012}).
\\\\
This section on gamification has thus discussed what gamification entails and how it usually implemented. A focus on the types of knowledge it is able to gamify is also presented as well as one way to effectively teach that type of knowledge. The following section will discuss existing attempts at producing a gamified system and serious games.

@@

\section{Potential Effects of Game-Based Learning}
Lastly, this section will document various and effects of using game-based learning in an attempt to ensure the framework of qualities and principles developed can avoid introducing them into the system that will be developed. Specifically, this section will focus on several studies that discuss the effect of games or elements of games. 
\\\\
With the implementation of games as a means of learning, positive effects are wanted over others. A study had developed a digital game to illustrate the executive function of being able to switch attention from one task to another effectively and quickly and found that participants that had several hours of playtime performed better on cognitive tests that tested the aforementioned skill (\cite{Mayer2019}). This study also found that the increase in cognitive skills had not happened in some games but had in others, although they do not mention which games these are (\cite{Mayer2019}). 
\\\\
A study by Kristiadi et al. (2019) found that games that have an element of adventure to them tend to cause and develop positive behaviour in those who played them. This is, however, dependent on several other requirements as well such as representation based on knowledge morality, ethics and cooperation (\cite{Kristiadi2019}). 
\\\\
Mertala and Meriläinen (2019) conducted a study into what type of games children were most interested in and talked about in a meaningful way. The study found a few key influential games that most children mentioned, the most notable being Minecraft and Super Mario (\cite{Mertala2019}). The study goes on to discuss the “ideal game” that each child designed through a drawing and it is clear that, as with the aforementioned influential games, they are all vibrantly colourful (\cite{Mertala2019}).
\\\\
Wouters et al. (2013) conducted a meta-analysis into the motivational effects of serious games and as such discuss various motivation based theories. It was found that serious games are a more effective means of instruction than other contemporary methods (\cite{Wouters2013}). Wouters et al. (2013) also found that the motivation of the participants making use of the game was not statistically more significant than those using traditional methods. One reason for this may be found in an explanation of the self-determination theory of motivation, which links to intrinsic motivation defined above in this literature review (\cite{Wouters2013}).
\\\\
Gomez et al. (2019) conducted a study into what effects prolonged exposure to playing a popular game franchise, Pokémon, as a child would have later in life as an adult. The study made use of several images and took images of the brain’s activity in participants while showing them these different images, examples of these pictures are shown below in the figure (\cite{Gomez2019}). The study found that people who did play Pokémon extensively as children, had different activity in their visual cortex when looking at the image of a Pokémon as compared to the other images in addition to the other participants, those who had no interaction with Pokémon growing up, had almost no activity when looking at images of Pokémon (\cite{Gomez2019}). Gomez et al. (2019) suggest that during the period of early development that participants were exposed to Pokémon is also when the brain is most responsive to visual stimuli.

>>>>

\noindent This current paradigm of education is operated based on standardisation to accommodate the change in societal needs and requirements that the industrial age brought with it (\cite{Reigeluth1996}). Reigeluth (1996) states that this system was developed on the fundamental need of sorting students into different categories and to allow for comparisons so that the training of the workforce could also be separated into different groups, those being labourers, having “hands-on” skills, and managers, who mainly had a managerial skill set. 
\\\\
However, with the shift into the “information age”, the requirements of the workforce have also changed. The industrial age being a time of mass-production with the emergence of various new processing technologies and the information age being characterised by the fact that information is being transmitted and generated at an ever-increasing rate due to further technological developments (\cite{gibson2006games, Reigeluth1996}). The most notable changes from the aforementioned paradigm shifts are that from conformity and compliance to initiative and diversity where greater value is placed on each individual’s strength and contribution to a project or organisation rather than each individual having the same skill set (\cite{Reigeluth1996}).  A few other differences between the needs of organisations during the industrial age and the new requirements brought with the information age are depicted in the above table.
\newpage
\noindent Reigeluth (1996) continues and states that the current paradigm is not focused on learning but rather categorisation. Ackoff (1991) hold a similar viewpoint stating that there is more of a focus on teaching rather than learning. It should be noted that teaching and learning are very distinct from one another as both can take place without the other (\cite{Ackoff1991}). Learning is defined as increasing one’s ability to perform an act effectively while trying to meet an objective through acquiring new knowledge whereas teaching is the process of providing this knowledge (\cite{Ackoff1991}). Through this, it is clear that institutions under this paradigm aim to give learners a verbose vocabulary to speak on topics that they do not fully comprehend (\cite{Ackoff1991}). 
\\\\
Due to this aforementioned paradigm shift and in what requirements are desired by most organisations in the information age, a shift in instructional theory is also needed – one such as going from making use of passive learning through traditional teaching means to one that is centred on active learning (\cite{Reigeluth1996}). These changes are discussed in more detail in the following section on pedagogy and learning theories and the means to accomplish them in the further sections on ludology and gamification.

@@

\subsection{Learners at Core of Learning}
Some instructional theories focus on students learning with minimal interaction with a teacher or instructor. Reigeluth (1996) refers to the learning methods that follow his ideology as ones where an instructor acts as an indirect guide to a class of learners instead of the typical “sage on the stage” structure of a lecture or presentation. 
\\\\\\
Two of these aforementioned theories are learning by doing and learning by teaching methods. Learning by doing functions on the principle that skills can be improved through practice and self-perfection on a particular topic or knowledge base (\cite{Fisch2009}). This means of instruction has become increasingly popular amongst companies where they are able to make use of “on the job” training as it allows for a person to be productive immediately as well as become more proficient at tasks gradually (\cite{Fisch2009}). The learning by teaching method works under the assumption that learners are able to increase their understanding of a certain topic by teaching it to other learners (\cite{Fisch2009}). This method of learning has garnered more usage recently as it is a viable means of learning in environments with too few teachers or instructors and increases the overall learning process (\cite{Fisch2009}). As shown in the following table, learning methods that place the learner in control are very flexible and as such can be incorporated when attempting to teach various and different fields or subjects (\cite{Ackoff1991}).

@@

\noindent The third principle, Demonstration, proposes that learning takes place when the activities that are undertaken impart the knowledge instead of stating the information (\cite{Merrill2002}). “Demonstration consistency” explains that any examples or visualisation should be kept in line with the original learning goals (\cite{Merrill2002}). The next is “Learner Guidance” and states that learners should be shown where the relevant information for problems can be found be it in the form of comparative examples or various representations of one source (\cite{Merrill2002}). “Relevant Media” explains that when media is used as a means of demonstration, different types can be used provided that they do not fight for a learner’s attention (\cite{Merrill2002}).
\\\\
The fourth principle is Application which states that learning takes place when learners actively solve problems with the new knowledge they have acquired (\cite{Merrill2002}). “Practice Consistency” is similar to Demonstration consistency but with a focus on the application of knowledge (\cite{Merrill2002}). “Diminishing Coaching” is where the learners are provided with relevant feedback, but it is slowly lessened over time (\cite{Merrill2002}). It is also important that the problems provided to learners for practice have a good variety, as explained as “Varied Problems” (\cite{Merrill2002}).
\\\\
The fifth, and final, principle is Integration which is when the knowledge a learner has acquired is used by them in their everyday life (\cite{Merrill2002}). The first corollary, “Watch Me”, explains that learners are provided to showcase the new knowledge or skill they have acquired (\cite{Merrill2002}). “Reflection” deals with giving learners time to be able to debate with others on the topic involved (\cite{Merrill2002}). Lastly, “Creation” states that learners should be able to make use of their new knowledge or skill in some personal capacity (\cite{Merrill2002}).
\\\\
The principles and corollaries provided by Merrill (2002) provide an expansive and detailed structure to be used when developing any learning opportunity making it an exceptional choice to adapt specifically to a digital game learning system.  It does, however, lack a comprehensive discussion on how to keep learners engaged with the content and, as such, the next subsection will discuss some theories pertaining to the role of motivation in learning.

@@

\subsection{Influence of Motivation}
A learner's motivation is what will drive them to engage with and enjoy the content being studied. This motivation can come in one of two forms according to Kapp (2012a) and to better understand the theories focussed on learner motivation, this distinction will be discussed first.
\\\\
The first is intrinsic motivation which is any motivation aimed to accomplish something and has originated from a desire to do something for oneself (\cite{Kapp2012a}). Thus, the motivation comes from the learner. On the other hand, with extrinsic motivation, the drive and desire to accomplish a task of some kind stems from wanting some form of reward or avoiding punishment of some kind (\cite{Kapp2012a}). Thus, motivation is created in return for something, either tangible or otherwise. 
\\\\
One model for motivating learners is the ARCS Model which was developed by John Keller (1987) which is frequently referenced in the aforementioned field of instructional design (\cite{Kapp2012a}). It is comprised of four main elements with each focusing on designing instruction in a different way (\cite{Kapp2012a, keller1987development}). 
\\
The first of these is Attention and it is an element that is concerned with gaining and then keeping the learners’ interest. There are three main methods to accomplish this with the first being gaining attention through the use of relatable examples or surprise. The next is to create curiosity within the learners through means such as role-playing or hands-on examples. The last means to keep attention is the variability which means periodically changing the method of delivery (\cite{Kapp2012a, keller1987development}).
\\\\
Relevance refers to having the content be relevant to the learner and Kapp (Kapp2012a) mentions that this can be done through orienting the environment around achieving goals, creating a link between the motives of learners and that of the instruction means, displaying that the content is in somewhat familiar to the learners and finally developing a model of the results of learning the presented knowledge (\cite{keller1987development}).
\\\\
Another element of this model, Confidence, is the expectations of success set by the learner and as such when they meet these expectations they are confident in their ability to do the work (\cite{Kapp2012a, keller1987development}). This can be aided by providing learners with clear expectations and requirements upfront about the skill or knowledge. It is also helpful to provide smaller opportunities to succeed as with each success the learners will become more confident (\cite{Kapp2012a, keller1987development}).
\\\\
The last element in the ARCS model is Satisfaction and is concerned with giving learners a sense of accomplishment and that the effort in the learning process has some value and weight to it (\cite{Kapp2012a, keller1987development}). This can be accomplished by allowing learners to see how their new-found knowledge can be used, either through the use of a real-world demonstration or via some form of simulation (\cite{Kapp2012a, keller1987development}).
\\\\
This section has detailed three aspects found within pedagogy, instructional design and learning theories each providing some insight into effectively transferring and imparting knowledge to a learner. Placing the learner at the centre of both teaching and learning allows for great flexibility in how to present that given material while Merrill (2002) provides an expansive framework to structure this presentation of knowledge whereas Kapp (2012a), through citing John Keller, explains ways to keep learners motivated throughout the learning process.

@@

\subsection{Serious Games}
Annetta (2008) states that the movement to include video games in teaching and training began in 2003, two years after the field of ludology began to gain traction itself concerning digital and computer-based games. The types of games used in this context are often referred to as “serious games”.  
\\\\
“Serious games” were introduced as digital concepts in 2002 through the Serious Game Initiative which was spearheaded by David Rejeski and Ben Sawyer (\cite{DeGloria2014}). The initial intention for serious games was for them to be used as a means of training certain tasks and skills (\cite{DeGloria2014}) – this was typically done through simulation type games which will be discussed in the following subsection in greater detail.
\\\\
Virvou, Katsionis and Manos (2005) mention that the endeavour to create serious games has yet to reach schools due to certain criticisms about games in general that hinders this. This is due to the fact that discussions around games by educators have largely focused on the social consequences of playing games instead of the educational potential games hold (\cite{Squire2003}). Due to this the study of serious games became more theoretical and discussion-based at lower levels and more applied with actual use at higher levels. This can be seen by implementations implemented in several fields including medical rehabilitation, ecological studies, learning languages and business studies (\cite{Burke2009, Costanza2014, Ranalli2008, Tao2009}). 
\\\\
These types of games have already had an impact on the military, medical and higher business education fields early in their conception and this trend continues to this day with most serious games being used within the medical fields specifically (\cite{Annetta2008, DeGloria2014}). However, there were attempts to use serious games, like simulations, within physics and engineering (\cite{Deshpande2011}).

\subsection{Games as Simulation}
Games have also found uses as a means to simulate models, environments and a myriad of other systems. As mentioned in the previous subsection, there are a few games used for medical training (\cite{Burke2009}) and to be effective at teaching and demonstrating these topics, digital games need to be used as a simulation.
\\\\
Squire (2003) provides a definition for games as a simulation and states that these simulations attempt to model reality in a consistent manner usually through modelling physical or social systems through another system – which in this case would be a computer and the digital video game. There are two main types of simulations, Hi-fidelity and low fidelity. Hi-fidelity simulations attempt to model every possible interaction in a given system, phenomena or environment as accurately as possible (\cite{Squire2003}). In contrast, a low fidelity simulation will make use of a fair bit of abstraction as it aims to only demonstrate a few key characteristics of the phenomena or environment (\cite{Squire2003}). Games as simulations would comprise of both of these types depending on the content that it attempts to simulate,
\\\\
Deshpande and Huang (2011) describe the use of games as a means of simulation for specific sections of work in physics and engineering courses as an addition to traditional teaching as it provides a relatively simple way to demonstrate certain phenomena. As such these authors discuss the simulation aspect of games rather than the narrative as when dealing with a simulation digital game it typical lacks most narrative elements in the traditional sense (\cite{Deshpande2011}).
\\\\
This section detailed the field of ludology and its roots in the “spirit of play” amongst cultures and society as well as the shift into being an academic means to study digital computer games. Through this, it was able to describe and develop the idea of a “serious game” and consequently games as simulations which are the most effective means to convey a learning environment through video games as a whole. Following this section, this study discusses how to link the learning theories of the previous section and the study of games together through a specific discussion on gamification.

@@

\item Psychomotor Domain deals with making use of cognitive knowledge through physical skills (hand-eye coordination is an example of this) and is most effectively taught through observation.
\end{itemize}
Gamification makes use of several procedures and processes that are rooted in various academic theories, most notably ones found within pedagogy and as such was discussed in the pedagogy section of this literature review (\cite{KappArticle2012}).
\\\\
This section on gamification has thus discussed what gamification entails and how it is usually implemented. A focus on the types of knowledge it is able to gamify is also presented as well as one way to effectively teach that type of knowledge. The following section will discuss existing attempts at producing a gamified system and serious games.

@@

\section{Potential Effects of Game-Based Learning}
Lastly, this section will document various and effects of using game-based learning in an attempt to ensure the framework of qualities and principles developed can avoid introducing them into the system that will be developed. Specifically, this section will focus on several studies that discuss the effect of games or elements of games. 
\\\\
With the implementation of games as a means of learning, positive effects are wanted over others. A study had developed a digital game to illustrate the executive function of being able to switch attention from one task to another effectively and quickly and found that participants that had several hours of playtime performed better on cognitive tests that tested the aforementioned skill (\cite{Mayer2019}). This study also found that the increase in cognitive skills had not happened in some games but had in others, although they do not mention which games these are (\cite{Mayer2019}). 
\\\\
A study by Kristiadi et al. (2019) found that games that have an element of adventure to them tend to cause and develop positive behaviour in those who played them. This is, however, dependent on several other requirements as well such as representation based on knowledge morality, ethics and cooperation (\cite{Kristiadi2019}). 
\\\\
Mertala and Meriläinen (2019) conducted a study into what type of games children were most interested in and talked about in a meaningful way. The study found a few key influential games that most children mentioned, the most notable being Minecraft and Super Mario (\cite{Mertala2019}). The study goes on to discuss the “ideal game” that each child designed through a drawing and it is clear that, as with the aforementioned influential games, they are all vibrantly colourful (\cite{Mertala2019}).
\\\\
Wouters et al. (2013) conducted a meta-analysis into the motivational effects of serious games and as such discuss various motivation based theories. It was found that serious games are a more effective means of instruction than other contemporary methods (\cite{Wouters2013}). Wouters et al. (2013) also found that the motivation of the participants making use of the game was not statistically more significant than those using traditional methods. One reason for this may be found in an explanation of the self-determination theory of motivation, which links to intrinsic motivation defined above in this literature review (\cite{Wouters2013}).
\\\\
Gomez et al. (2019) conducted a study into what effects prolonged exposure to playing a popular game franchise, Pokémon, as a child would have later in life as an adult. The study made use of several images and took images of the brain’s activity in participants while showing them these different images, examples of these pictures are shown below in the figure (\cite{Gomez2019}). The study found that people who did play Pokémon extensively as children, had different activities in their visual cortex when looking at the image of a Pokémon as compared to the other images in addition to the other participants, those who had no interaction with Pokémon growing up, had almost no activity when looking at images of Pokémon (\cite{Gomez2019}). Gomez et al. (2019) suggest that during the period of early development that participants were exposed to Pokémon is also when the brain is most responsive to visual stimuli.
